### 2022-06-28 input/experiments.tex
meow

\subsection{Traffic containment}
\item [Objective:] Confirm that \NAME locks down the traffic of
  decentralized content indexing in the context of dynamic
  inter-autonomous system communications.

@@

\noindent Finally, Figure~\ref{fig:geant} shows that, when adding back the
inter-continental link, the two clusters can communicate again. In the
experiment involving one source for two clusters, it generates
traffic. After a $200$ milliseconds delay corresponding to the inter-continental link
latency, the cut off cluster starts to communicate $\alpha$ messages
again. Eventually, all \processes belong to the same
partition. However, in the experiment involving one source \emph{per}
cluster, the new link does not trigger noticeable traffic, for
\processes already know their closest source located in their cluster.

>>>>

\subsection{Traffic containment}
\item [Objective:] Confirm that \NAME locks down the traffic of
  decentralized content indexing in dynamic
  inter-autonomous systems.

@@

\noindent Finally, Figure~\ref{fig:geant} shows that, when adding back the
inter-continental link, the two clusters can communicate again. In the
experiment involving one source for two clusters, it generates
traffic. After a $200$ milliseconds delay corresponding to the inter-continental link
latency, the cut off cluster starts to communicate $\alpha$ messages
again. Eventually, all \processes belong to the same
partition. However, in the experiment involving one source \emph{per}
cluster, the new link does not trigger noticeable traffic, for
\processes already know their closest source in their cluster.
